### 2025-09-23 paper/sec/authoring-workflow.tex
Some progress on workflow. Need a bit of decomposition though.

Figure~\ref{fig:overall-architecture} shows the system architecture and an example flow.
The system is composed of two LLM-based agents:

@@

The author initially imports the text and accompanying data into the system, which creates a Fluid
representation of the target document. Initially that representation is just a string literal of the form
\kw{"""..."""}, where the triple quotes are the Fluid syntax for an \emph{interpolated string}, i.e.~a string
literal where expressions of the form \kw{\{$e$\}} are permitted within the string. The \SuggestionAgent
analyses the inputs and identifies candidate fragments of natural language which could be replaced by Fluid
expressions. Figure~\ref{fig:interpretation-agent} then shows the human-in-the loop workflow of the
\InterpretationAgent. The entry point is the selection by the author of a fragment of text $s$ to interpret, a
fragment which may or may not have been highlighted previously by the \SuggestionAgent. The system then
generates a candidate Fluid expression $e$ by prompting the LLM (\secref{prompt-design} below). The expression
is validated through a closed loop program synthesis step to check that it is well-formed, and, if so, that it
evaluates to the target fragment of text $s$. If $e$ indeed evaluates to $s$, then the system replaces $s$ in
the original top-level string with the interpolation expression \kw{\{$e$\}}. This is the primary successful
path through the loop and returns the system to the ideal state where it is waiting for another top-level
interaction from the author.

Otherwise, the Fluid command-line either returned an error (either a syntax error or runtime error), or it
succeeded but $e$ evaluated to some other string $s' \neq s$. Both cases trigger prompt augmentation with an
appropriate error message, and the system retries generation. In cases where the expression remains invalid or
mismatched, the user may intervene by resolving the mismatch manually or rejecting the candidate. Once a valid
expression is approved, the updated text is spliced back into the document, and any downstream interactions
(e.g. reloading the web page) are checked. This closed-loop design combines automated synthesis with
validation and author oversight, ensuring both correctness and usability of the generated code.

>>>>

Our authoring tool is composed of two LLM-based agents:

@@

The author initially imports the text and accompanying data into the system, which creates a Fluid
representation of the target document. Initially that representation is just a string literal of the form
\kw{"""..."""}, where the triple quotes are the Fluid syntax for an \emph{interpolated string}, i.e.~a string
literal where expressions of the form \kw{\{$e$\}} are permitted within the string. The \SuggestionAgent
analyses the inputs and identifies candidate fragments of natural language which could be replaced by Fluid
expressions. The system then enters the human-in-the loop workflow shown in
Figure~\ref{fig:interpretation-agent}, where the author interacts with the \InterpretationAgent. The system is
initially waiting for the author to select a fragment of text $s$ to interpret, a fragment which may or may
not have been highlighted previously by the \SuggestionAgent. The system then generates a candidate Fluid
expression $e$ by prompting the LLM (\secref{prompt-design} below). The expression is validated through a
closed loop program synthesis step which checks that it is well-formed and evaluates to the target fragment
$s$. If this process succeeds, the system replaces the selected substring $s$ with the interpolation
expression \kw{\{$e$\}}, creating a new document configuration. This is the primary successful path through
the workflow and returns the system to the entry state where it is waiting for another top-level interaction
from the author.

Otherwise, the Fluid command-line either returned an error (either a syntax error or runtime error), or
succeeded but $e$ evaluated to some other string $s' \neq s$. Both cases trigger prompt augmentation with an
appropriate error message, and the system retries generation. Failure of the code synthesis step means that,
even after multiple retries with an augmented prompt, $e$ remained invalid or evaluated to $s' \neq s$. If $e$
was invalid (resulting in an error), no remedial action is open to the author. This is considered an
unsuccessful path through the workflow and returns the system to the start state. In the $s' \neq s$ case, the
can choose to manually abort and return to the entry state, or optionally to \emph{revise the goal}, replacing
$s$ with $s'$ in the target document and retaining $e$ as the candidate expression. This is intended to cover
the situation where the author has made a claim which is \emph{incorrect}, but the data set and surrounding
natural language has caused the LLM to synthesise an expression which generates a different value from the one
specified by the user. Once a valid expression is approved, the updated text is spliced back into the
document, and any downstream interactions (e.g. reloading the web page) are checked. This closed-loop design
combines automated synthesis with validation and author oversight, ensuring both correctness and usability of
the generated code.
